---
title: "Initial Korean covid 19"
author: "Luis Resendez"
date: "Summer 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```

#Introduction



### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female  
77 of the data entries were coded sex  as blank, so we omit these.  
state of a patient must be died or alive - we adjust that as well      
  
# Your Question - Is dying independent of sex?

$H_0$:
There is no difference between death rates depending upon sex.

$H_A$: There is a difference between death rates depending upon sex.

# Methods

result is a categorical variable, sex is categorical  
result depends on sex , we use a helper file  
cat~cat  



# Results

## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

  This bar chart shows that more women lived than died. It also shows that more men died over women. 





  
## Numerical results

```{r}
table2 <- xtabs(~result + sex, data=kRdata)
rowPerc(table2)
colPerc(table2)
```
This numerical summery shows that more males died as apposed to women.  


## Inferential results 


## Inferential  

```{r}
chisq.test(table2)
chisqtestGC(table2)
fisher.test(table2)
```

The P- Value for the chi score test is 0.001, so we reject the null hypothesis that and death by Covid is related.

The fisher exact test shows that men are 2.3 times more likely to die than women in Korea.




## Conclusions


In conclusion we must reject the null hypothesis that Covid deaths between men and women are not dependent on sex. The p value states the results were to small to indicate a difference in sex.

