---
title: "Initial Korean covid 19"
author: "Luis Resendez"
date: "Summer 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```

#Introduction



### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female  
77 of the data entries were coded sex  as blank, so we omit these.  
state of a patient must be died or alive - we adjust that as well      
  
# Your Question - Is dying independent of sex?


# Methods

result is a categorical variable, sex is categorical  
result depends on sex , we use a helper file  
cat~cat  



# Results

## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

  This bar chart shows that more women lived than died. It also shows that more men died over women. 





  
## Numerical results

```{r}
table2 <- xtabs(~result + sex, data=kRdata)
rowPerc(table2)
colPerc(table2)
```
This numerical summery shows that more males died as apposed to women.  


## Inferential results 




## Conclusions

